A Survey Wearable Device Risk Perceptions

### 2015-01-05 wearables_survey.tex
Edited Related Work

\subsection{Ubiquitous Sensing}
At an unprecedented rate, we are moving towards automated capture and ubiquitous access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables. Wearbles have new capabilities which allow capture of unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security concerns ~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved my adhering to principles such as notice, choice, and consent ~\cite{langheinrich2001privacy}.

\subsection{Smartphones and Wearables Concerns}
There exists work which addresses anticipated privacy and security challenges related to mobile and wearable devices from a system standpoint, such as \cite{DiPietro}. However, works like these are not grounded in user research and do not make claims about what the the most relevant concerns for the average user are. Felt et. al's study of smartphone user concerns \cite{Felt} was the first to investigate the smartphone security and privacy landscape from a user study standpoint. The survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a likert scale ranging from indifferent (1) to very upset (5). Our work is motivated by this mobile study, and aims to also investigate wearables security and privacy with a user focus to find the most relevant challenges. We use a similar scale to ask our users how upset they would be if a certain action was taken without their permission, but ask questions about new capabilities on wearable devices. To our knowledge, our work is the first of its kind to investigate such user concerns.

\subsection{Technology Risk Perceptions}
While evaluating which are the most pressing concerns for users, it is also important to take into account how users' perception of particular technology. A seminal risk-benefit analysis psychometric study by Fischoff \cite{Fischhoff} studied how 76 users perceived the risks and benefits of 30 activities and technologies. In the study, participants were prompted to rate the risks and benefits of 30 activities and technologies for all people affected by the technology, for a long period of time. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). In our survey, we use a similar prompt to ask participants to rate the risks and benefits of 20 new technologies. Denning et. al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}. Bystanders expressed concerns due to the subtle, easy-to-use, and prevalent nature of wearables. While people have conducted studies on privacy concerns with respect to wearables, we are aware of no work which as looked at privacy perspectives of the owner of the device. In our survey, we show how risk and benefit perception plays a role in how users perceive various new devices and new technologies in wearables.

\subsection{Crowdsourced User Studies}
Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}. While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S. population \cite{ross2010crowdworkers}\cite{kelley2010conducting}. Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S. public \cite{kang2014privacy}.

>>>>

\subsection{Ubiquitous Sensing}
Due to new technological advances, we are rapidly moving towards automated capture and ubiquitous data access~\cite{abowd2000charting}, whether it be through smartphones, smarthomes, networked devices, or, more recently, wearables. Wearables have new capabilities that allow capture of unique data about the user and his/her surroundings. As information capture becomes pervasive and subtle, people are naturally concerned about privacy and security~\cite{palen2003unpacking}. Privacy in ubiquitous systems can be achieved by adhering to principles such as notice, choice, and consent~\cite{langheinrich2001privacy}.

\subsection{Smartphones and Wearables Concerns}
%I really don't know what this first sentence means...

Much of the previous work addresses the anticipated privacy and security challenges related to mobile and wearable devices from a systems standpoint (e.g.,~\cite{DiPietro}). However, system designs to improve end-user security need to be grounded in user research to better understand end-user concerns. Felt \etal were among the first to examine the security concerns of smartphone users using a large-scale online survey~\cite{Felt}. Their survey asked 3,115 smartphone users about 99 risks associated with various smartphone privileges. Participants were asked how upset they would be if a certain action had occurred without their permission. Participants rated each situation on a Likert scale ranging from ``indifferent (1)'' to ``very upset (5).'' Our work builds upon this study, by aiming to evaluate the types of concerns that users have surrounding future wearable device capabilities, and then to compare those concerns to concerns surrounding more established technologies.

Denning et. al conducted a study investigating privacy perspectives the bystanders of wearable devices ~\cite{Denning2014}. Bystanders expressed concerns due to the subtle, easy-to-use, and potentially ubiquitous nature of wearables. While this research examined the privacy concerns of bystanders in the presence of wearable devices, we are aware of no work that has looked at the privacy concerns of the owners of the devices.

\subsection{Technology Risk Perceptions}
Fischhoff \etal performed a seminal technology risk perception experiment in which they studied how people perceived the risks and benefits of 30 common activities and technologies~\cite{Fischhoff}. In their study, participants were prompted to separately rate the risks and benefits of 30 activities and technologies. They were primed to think about all people affected by the technology, and to think about long-term vs. short-term risks and benefits.. The participants rated these technologies with respect to each other on a numerical scale, being instructed to rate the least risky or least beneficial technology a 10 and scaling the ratings linearly (i.e. a technology with risk rating 20 would be considered twice as risky compared to a technology with a risk rating of 10). Using this mythology, they were able to categorize different technologies based on whether they were high-risk/high-benefit, low-risk/low-benefit, and so forth.

%I'm not sure that having a background on crowdsourcing is relevant, especially given the space limitations. Instead, you need WAY more related work on ubiquitous privacy concerns, as well as smartphone privacy concerns. There's also probably more general work on risk perceptions that should probably be cited.

%\subsection{Crowdsourced User Studies}
%Crowdourcing user studies in Mechanical Turk has its challenges \cite{kittur2008crowdsourcing}. While the Amazon Mechanical Turk population is diverse across several significant demographic dimensions such as age, gender, and income, it is not a precise representation of the U.S. population \cite{ross2010crowdworkers}\cite{kelley2010conducting}. Additionally, Amazon Mechanical Turk workers generally put a higher value on anonymity and hiding information, were more likely to do so, had more privacy concerns than the larger U.S. public \cite{kang2014privacy}.
